---
title: "Initial Korean covid 19"
author: "Roxan Barakat"
date: " Spring 2023"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?






## Graphical results - use ggplot commands to do this  
```{r}
barchartGC(~result + Sex, data=kRdata)
barchartGC(~result + Sex,data=kRdata, type = "percent")
```
The models above provide a representation of the disease killing males and females. The order is formed from the percent of a frequency of males and females. Here the percent of people who are dying the most is the men group. This is why graphs between the men and women are not evenly distributed. 

## Numerical results
```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```
The numerical results provide a further representation of the disease killing more males than females. This is way the results between men and women are not evenly distributed. The results say 56 females lived over 44 males in a 100 total sample and 36 females died and 64 males died in a 100 total sample.  

## Inferential results 




## Conclusions

